Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-20 prop_letter.tex
prop_letter.tex Updating interpertation...

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem*{example*}{Example}

@@

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
effect of finite-precision uncertainties on measurement outcomes,
reducing to the purely deterministic Kochen-Specker case for
$\delta=0$, can resolve the question of the effect of finite precision
and imperfections on contextuality.  A remarkable consequence of our
analysis is that not only does the quantum-mechanical requirement for
contextuality continue to hold, thus maintaining the Kochen-Specker
result for a \emph{non-vanishing} range of $\delta$, but that at a
\emph{certain fixed value} of $\delta$, there is a sharp transition,
parallel in its consequences to, say, a phase transition, to
\emph{non-contextuality}; that is, suddenly a quantum system can be
simulated by a non-contextual hidden variable theory, turning the
system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
\yutsung{Still not comfortable about the current statement... Notice
that the key properties of the non-contextual hidden variable theory
used in our Mermin-Peres square proof is
\begin{itemize}
\item The expectation value of an observable is one of the eigenvalue of
that observable.
\item For $0$-deterministic QIVPMs, we have
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
\end{itemize}
I think these two properties might be weakened when $0<\delta<\frac{1}{3}$,
and completely break down when $\delta\ge\frac{1}{3}$. (Need a proof!)
If this is the case, the correct statement is that ``the assumption
of non-contextuality hidden variable theory could be considered hold
when $\delta<\frac{1}{3}$, and is completely void when $\delta\ge\frac{1}{3}$.''
So we should not even ask ``whether the existence of QIVPMs when
$\delta\ge\frac{1}{3}$ implies non-contextuality hidden variable
theory or not.'' A little bit different analog could be: we should
not ask ``where is the momentum of a particle when we measure its
position...''}

>>>>

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{assumption}{Assumption}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem*{example*}{Example}
\newtheorem{condition}[assumption]{Condition}

@@

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
effect of finite-precision uncertainties on measurement outcomes,
reducing to the purely deterministic Kochen-Specker case for
$\delta=0$, can resolve the question of the effect of finite precision
and imperfections on contextuality.  A remarkable consequence of our
analysis is that not only does the quantum-mechanical requirement for
contextuality continue to hold, thus maintaining the Kochen-Specker
result for a \emph{non-vanishing} range of $\delta$, but that at a
\emph{certain fixed value} of $\delta$, there is a sharp transition,
parallel in its consequences to, say, a phase transition, to
\emph{non-contextuality}; that is, suddenly a quantum system can be
simulated by a non-contextual hidden variable theory, turning the
system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
\yutsung{Still not comfortable about the current statement... To
clarify what we did, here we review the assumption in the original
Kochen-Specker theorem, and what we used in our variant version.}

The original Kochen-Specker theorem assumes the following there is
a hidden variable assignment~$v$ for every observables~$\mathbf{O}$
such that

\begin{assumption}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$ are
commuting, then $v$ is linear, i.e., $v\left(x_{0}\mathbf{O}_{0}+x_{1}\mathbf{O}_{1}\right)=x_{0}v\left(\mathbf{O}_{0}\right)+x_{1}v\left(\mathbf{O}_{1}\right)$
for $x_{0}$ and $x_{1}\in\mathbb{C}$.\end{assumption}

\begin{assumption}\label{assu:times}If $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$
are commuting, then $v\left(\mathbf{O}_{0}\mathbf{O}_{1}\right)=v\left(\mathbf{O}_{0}\right)v\left(\mathbf{O}_{1}\right)$.\end{assumption}

\noindent These two assumptions implies the following conditions:

\begin{condition}\label{cond:eigenvalue}$v\left(\mathbf{O}\right)$
must be an eigenvalue of $\mathbf{O}$.\end{condition}

\noindent In particular, Condition~\ref{cond:eigenvalue} implies
$v(P)=0$ or $1$ for any projector~$P$. Together with $v\left(\mathbb{1}\right)=1$.
We have:

\begin{condition}\label{cond:sum-one}If a set of commuting projectors~$P_{i}$
satisfies $\sum_{i}P_{i}=1$, then $\sum_{i}v(P_{i})=1$.\end{condition}

\noindent Kochen-Specker~\citep{kochenspecker1967} and Peres~\citep{peres1995quantum}
then proved the contradiction based on Condition~\ref{cond:sum-one}.
The proof given by Mermin~\citep{Mermin1990Simple} is particular
short and easy to understand, because he proved proved the contradiction
based on Assumption~\ref{assu:times} and Condition~\ref{cond:eigenvalue}.

\yutsung{Let's move on to what we did for 0-Deterministic Variant
of Kochen-Specker theorem~\ref{thm:Kochen-Specker}.}

\yutsung{Finally, we can say about Finite-precision Extension of
Kochen-Specker theorem~\ref{cor:Kochen-Specker-IVPM}.}

Notice that the key properties of the non-contextual hidden variable
theory used in our Mermin-Peres square proof is
\begin{itemize}
\item The expectation value of an observable is one of the eigenvalue of
that observable.
\item For $0$-deterministic QIVPMs, we have
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
\end{itemize}
I think these two properties might be weakened when $0<\delta<\frac{1}{3}$,
and completely break down when $\delta\ge\frac{1}{3}$. (Need a proof!)
If this is the case, the correct statement is that ``the assumption
of non-contextuality hidden variable theory could be considered hold
when $\delta<\frac{1}{3}$, and is completely void when $\delta\ge\frac{1}{3}$.''
So we should not even ask ``whether the existence of QIVPMs when
$\delta\ge\frac{1}{3}$ implies non-contextuality hidden variable
theory or not.'' A little bit different analog could be: we should
not ask ``where is the momentum of a particle when we measure its
position...''

\yutsung{End of discussion!}
